\documentclass[a4paper,11pt]{article}
%\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[margin=0.33in]{geometry}
\usepackage{enumitem}
\usepackage{tabto}
\usepackage{fontawesome5}
\titleformat{\section}
{\small \bfseries \uppercase}
{}
{-0.8em}
{}[\titlerule]
\titleformat{\subsection}
{\bfseries\Small}
{}
{0.0em}
{}
\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}
\titlespacing{\subsection}{0em}{0em}{0em}
\titlespacing{\subsubsection}{0em}{0em}{0em}
\setlist[itemize]{itemsep=0em}
\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries \uppercase
\theauthor}
\vspace{0em}
% {\small \normalfont (778) 917 -- 6940 --- vermak1996@outlook.com --- www.linkedin.com/in/vkunal1996 ---  https://github.com/vkunal1996 --- vermakunal.com --- Vancouver, BC, Canada}
\end{center}
}
\begin{document}
\color{darkgray}
\title{Resume}
\author{Kunal Verma}
\maketitle

%Introduction Section
\begin{center}
    \bfseries \faIcon{mobile-alt}\hspace{0.4em}(778)--917--6940\hspace{1.0em}  \faIcon{envelope}\hspace{0.4em}kunalverma2210@gmail.com \hspace{1.0em}
    \faIcon{linkedin}\hspace{0.4em}\href {https://www.linkedin.com/in/vkunal1996}{https://www.linkedin.com/in/vkunal1996} \hspace{1.0em} \faIcon{github}\hspace{0.4em}\href{https://www.github.com/vkunal1996}{https://www.github.com/vkunal1996}\hspace{1.4em}  
    \faIcon{globe}\hspace{0.4em}\href{https://www.vermakunal.com}{https://www.vermakunal.com}
\end{center}

% Employment Section
\section{Employment}
\subsection{Graduate Research Assistant \hspace{24em} Vancouver, CA}
\emph{Natural Language Processing Lab at The University of British Columbia \hspace{9.4em} Jun'20 --- Aug'20}
\begin{itemize}
    \item Collected \textbf{1 Billion Tweets} of \textbf{1 Million users} from \textbf{268 countries} in \textbf{104} different language using Twitter Python API.
    \item Performed Big Data operations using Apache Spark for analysis on human behaviour on social media before and during Covid-19 pandemic. 
    \item Investigated the inter state mobility and web site visiting behaviour of the users in 2020 comparing to 2019.
\end{itemize}
\subsection{Developer Intern          \hspace{29em}                                   Jalandhar, IN}
\emph{Itronix Solution \hspace {33em} Jan'19 --- Jun'19}
\begin{itemize}
    \item Developed a Web based application to predict the sentiments of the user feedback for an airline service.
    \item Deployed front end of the Web application using Python, Flask and JavaScript.
    \item Deployed the Machine Learning model as a flask API service to derive the sentiments from the user provided reviews and provided summary in the form of Dashboard. 
\end{itemize}

%Education Section
\section{Education}
\subsection{University of British Columbia \hspace{23em}                   Vancouver, CA}
\emph{Master of Engineering in Electrical and Computer Engineering \hspace{13.3em}         Sep'19 --- Jun'21}
% \begin{itemize}
%     \item Research Assistant @ Natural Language Processing Lab
% \end{itemize}
\vspace{0.1em}
\subsection{Guru Nanak Dev University   \hspace{24.2em}                        Jalandhar, IN}    
\emph{Bachelor of Technology in Computer Science and Engineering \hspace{13.7em}          Jun'15 ---  Jun'19}

% \begin{itemize}
%     \item Coding Head @ Technical Student Society and Engineering Student Society
%     \item Coding Contest Organizer @ Hackerearth.com
% \end{itemize}

% Projects Section
\section{Projects}
\subsection{\href{https://github.com/vkunal1996/CPEN400-ChatApp}{Client-Server Chat Application}}
\begin{itemize}
    \item Developed a client-server chat application using JavaScript, NoSQL, and NodeJS.
    \item Implemented the real time messaging service using the web socket module by which various clients can send/receive messages simultaneously.
\end{itemize}
\subsection{\href{http://knowyoursentiment.herokuapp.com}{Feedback Emotion Prediction}}
\begin{itemize}
    \item Developed and deployed a web based application using python, flask and JavaScript which predicts the sentiments of the customer's feedback for an airline service. 
\end{itemize}
\subsection{\href{https://github.com/vkunal1996/CodeHunt-Desktop-Based-Application}{Quiz Application}}
\begin{itemize}
    \item Developed a Java based Swing GUI application for programming quiz. Implemented multi threaded architecture for timer functionality.
    \item Programmed a random function to generate a unique code each time for a test session. 
\end{itemize}
\subsection{\href{https://arxiv.org/abs/2005.06012}{Mega-COV: A Billion-Scale Dataset of 100+ Languages for COVID-19}}
\begin{itemize}
    \item Investigated the User's behaviour on Twitter during pandemic and published the paper in \textbf{EACL2021} conference. 
\end{itemize}



%Skills Section
\section{SKILLS}
\subsubsection{Technical Skills: }\hspace{0.4em}Java, Python, JavaScript, {\LaTeX}, MySQL, MongoDB
\subsubsection{Framework and Tools: }\hspace{0.4em}NodeJS, ReactJS, NumPy, Pandas, Matplotlib, Flask, Spark(Python), Hibernate, Spring, Struts, JSF, JSP, Git, Heroku
\subsubsection{Interests: }\hspace{0.4em}Machine Learning, Natural Language Processing, Cloud Computing

% \section{Volunteering}
% \subsection{UBC NLP Group -  Member}
% \begin{itemize}
%     \item Crawling tweeter data for research purposes.
%     \item Operating \textbf{Word2Vec} and \textbf{FastText} models for big data operations.
%     \item Carrying out visual and graphical analysis to get the meaningful insights from the data
% \end{itemize}
\end{document}
