\documentclass[a4paper,11pt]{article}
%\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[margin=0.33in]{geometry}
\usepackage{enumitem}
\usepackage{tabto}
\usepackage{fontawesome5}
\titleformat{\section}
{\small \bfseries \uppercase}
{}
{-0.8em}
{}[\titlerule]
\titleformat{\subsection}
{\bfseries\Small}
{}
{0.0em}
{}
\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}
\titlespacing{\subsection}{0em}{0em}{0em}
\titlespacing{\subsubsection}{0em}{0em}{0em}
\setlist[itemize]{itemsep=0em}
\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries \uppercase
\theauthor}
\vspace{0em}
% {\small \normalfont (778) 917 -- 6940 --- vermak1996@outlook.com --- www.linkedin.com/in/vkunal1996 ---  https://github.com/vkunal1996 --- vermakunal.com --- Vancouver, BC, Canada}
\end{center}
}
\begin{document}
\color{darkgray}
\title{Resume}
\author{Kunal Verma}
\maketitle
\begin{center}
    \bfseries \faIcon{mobile-alt}\hspace{0.4em}(778)--917--6940 \textbullet\ \faIcon{envelope}\hspace{0.4em}vermak1996@outlook.com \textbullet\ \faIcon{linkedin}\hspace{0.4em}\href {https://www.linkedin.com/in/vkunal1996}{https://www.linkedin.com/in/vkunal1996} \textbullet\ \faIcon{github}\hspace{0.4em}\href{https://www.github.com/vkunal1996}{https://www.github.com/vkunal1996} \textbullet\ \faIcon{globe}\hspace{0.4em}\href{https://www.vermakunal.com}{https://www.vermakunal.com}
\end{center}
\section{Employment}
\subsection{Graduate Research Assistant \hspace{24em} Vancouver, CA}
\emph{Natural Language Processing Lab at The University of British Columbia \hspace{9.4em} Jun'20 --- Aug'20}
\begin{itemize}
    \item Collected \textbf{1 Billion Tweets} of \textbf{1 Million users} from \textbf{268 countries} in \textbf{104} different language using Twitter Python API.
    \item Inspected the inter-state mobility of the users in the US between January'20 to May'20
    \item Investigated the Rank change of the \textbf{top 40 most visited domains} in 2020 comparing to 2019
    \item Predicted the undefined languages using \textbf{langid}, \textbf{langdetect}, and \textbf{fasttext} models increasing the total number of detected languages from 67 to 100+ languages.
    \item Operated \textbf{AraNet} on \textbf{1 Billion Arabic Tweets} to predicts sentiments, dialect, irony and age-gender of the users.
\end{itemize}
% \subsection{Data Science Trainee                                             Jalandhar, IN}
% \subsubsection{\emph{Itronix Solution}}
% \begin{itemize}
%     \item 
% \end{itemize}
\section{Education}
\subsection{University of British Columbia \hspace{23em}                   Vancouver, CA}
\emph{Master of Engineering in Electrical and Computer Engineering \hspace{13.3em}         Sep'19 --- Jun'21}
% \begin{itemize}
%     \item Research Assistant @ Natural Language Processing Lab
% \end{itemize}
\vspace{0.8em}
\subsection{Guru Nanak Dev University   \hspace{24.2em}                        Jalandhar, IN}    
\emph{Bachelor of Technology in Computer Science and Engineering \hspace{13.7em}          Jun'15 ---  Jun'19}
% \begin{itemize}
%     \item Coding Head @ Technical Student Society and Engineering Student Society
%     \item Coding Contest Organizer @ Hackerearth.com
% \end{itemize}
\section{SKILLS}
\subsubsection{Technical Skills: }\hspace{0.4em}Java, Python, JavaScript, C++, HTML, CSS, BootStrap, {\LaTeX}
\subsubsection{Databases: }\hspace{0.4em}MySQL, MongoDB, firebase
\subsubsection{Framework and Tools: }\hspace{0.4em}NodeJS, ReactJS, NumPy, Pandas, Flask, Spark(Python), Hibernate, Spring, Struts, JSF, JSP, git, Heroku
\subsubsection{Interests: }\hspace{0.4em}Machine Learning, Natural Language Processing, Cloud Computing
\section{Projects}
\subsection{\href{https://arxiv.org/abs/2005.06012}{Mega-COV: A Billion-Scale Dataset of 100+ Languages for COVID-19}}
\begin{itemize}
    \item Research Paper accepted at EACL2021 conference.
    \item Generated a \textbf{Billion Scale} dataset to help researchers for studying pehnonmena related to pandemics.
    \item Collected more than \textbf{1 Billion Tweets} from 268 countries using Tweeter Python API.
    \item Researched and Examined the \textbf{top 20 languages} of the tweets.
    \item Coordinated to develop a BERT-Base Multilingual Case model for detecting tweets related to COVID-19 with a significant accuracy of 94\%.
\end{itemize}
\subsection{\href{https://github.com/vkunal1996/CPEN400-ChatApp}{Client-Server Chat Application}}
\begin{itemize}
    \item Developed a client-server chat application using JavaScript, NoSQL, and NodeJS.
    \item Examined different cross scripting attacks on the websites and sanitizing process to avoid such attacks.
    \item Coded the functionality of creating groups, fetching messages from the database server, and connecting clients to the server in order to send and receive messages.
\end{itemize}
\subsection{\href{http://knowyoursentiment.herokuapp.com}{Emotional Polarity Classifier}}
\begin{itemize}
    \item Developed a web based application using flask and python to predict the sentiments of the feedback given by customers to the airline services.
    \item Deployed and Evaluates different classical and deep learning models for the prediction process.
    \item Deployed the whole web application and models on the heroku platform.
\end{itemize}
% \section{Volunteering}
% \subsection{UBC NLP Group -  Member}
% \begin{itemize}
%     \item Crawling tweeter data for research purposes.
%     \item Operating \textbf{Word2Vec} and \textbf{FastText} models for big data operations.
%     \item Carrying out visual and graphical analysis to get the meaningful insights from the data
% \end{itemize}
\end{document}
